Multimodal Contrastive Learning for Object Retrieval in the Face of Modality Failures \\ Extended Multimodal Alignment \\ Combining Geometric and classification ...

### 2022-08-17 Paper/main.tex
first draft of paper for TMLR

\documentclass[sigconf,natbib=true,anonymous=true]{acmart}
% \documentclass[manuscript,screen,review]{acmart}

% Needed to fix an acmart problem with line numbering. AFAICT line 
% numbers are not expected in sigconf, so it should be a no-op.
\makeatletter
\providecommand{\@LN}[2]{}
\makeatother

% % Fonts used in the template cannot be substituted; margin 
% % adjustments are not allowed.
% %
% % \BibTeX command to typeset BibTeX logo in the docs
% \AtBeginDocument{%
%   \providecommand\BibTeX{{%
%     \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[SIGIR '22]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2022}{Madrid, Spain}
%
%  Uncomment \acmBooktitle if the title of the proceedings is different
%  from ``Proceedings of ...''!
%
\acmBooktitle{SIGIR '22: Proceedings of the 45th International ACM SIGIR Conference on Research and Development in Information Retrieval,
 July 11--15, 2022, Madrid, Spain} 
% \acmPrice{15.00}
% \acmISBN{978-1-4503-XXXX-X/18/06}

%
% Submission ID.
% Use this when submitting an article to a sponsored event. You'll
% receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
% \acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and
% references.  The command \citestyle{authoryear} switches to the
% "author year" style.
%
% If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of
% citations and references.
% Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \country{USA}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
% EDITING LINK: 
% https://www.overleaf.com/3575751412sjsdmszkxsyh
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

% \usepackage{soul} %% Soul does not play well with acmart
\usepackage{url}
% % \usepackage[hidelinks]{hyperref}https://www.overleaf.com/project/614b5cc61d38655dce466002
% \usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cleveref}
\usepackage{lipsum}

\urlstyle{same}

% % =======================================
% % my imported packages

\usepackage{amsmath}
\usepackage{bm}
% \usepackage{amssymb}          % duplicates something in acmart
\usepackage{listings}
% \usepackage[ruled,vlined]{algorithm2e}
\include{pythonlisting}

\newcommand{\pseudosection}[1]{\vspace{1.5ex}\noindent \textit{{#1:~~}}}
% \newcommand{\pseudosection}[1]\indent{{{}}}

\usepackage{todonotes}
\newcommand{\todokdinline}[1]{\todo[color=red!20,inline]{{KD: \small #1}}}
\newcommand{\todokd}[1]{\todo[color=red!20]{{\small #1 -- Kasra}}}
% \newcommand{\todocainline}[1]{\todo[color=yellow!20,inline]{{CA: \small #1}}}
\newcommand{\todocm}[1]{\todo[color=green!40]{\small #1 -- Cynthia}}
\newcommand{\todocmi}[1]{\todo[inline,color=green!40]{\small #1 -- Cynthia}}
\newcommand{\todoff}[1]{\todo[color=blue!20]{\small #1 -- Frank}}
\newcommand{\todoed}[1]{\todo[color=cyan!20]{\small #1 -- Ed}}

\newcommand{\CitationNeeded}[1]{{\textbf {\color{red}Cite #1}}}
\newcommand{\ProofRead}[1]{{\textbf {\color{red}Proofread please #1}}}
\newcommand{\Complete}[0]{{\textbf {\color{red}Complete it }}}
\newcommand{\Rephrase}[1]{{\textbf {\color{red}Rephrase please #1}}}

% \newcommand{\citet}[1]{\cite{#1}} % This is used because \citet didn't work with their author kit % It does now

% =======================================
\title{Multimodal Contrastive Learning for Object Retrieval in the Face of Modality Failures}

@@

% Todo list
% \begin{enumerate}
%     \item \st{Lit search}
% \end{enumerate}
% \newpage

% ***************** The BEGINNING of the paper *****************

@@

    We propose a generalized distance-based loss function that can be used to learn retrieval models that incorporate an arbitrary number of views of a particular piece of data, and compounded by the challenge of retrieval when a modality becomes unavailable. 
    Our study is motivated by needs in robotics and computer-human interaction, where an agent has many sensors and thus modalities in which a human may interact: voice, text, images, and depth, both to communicate a desired goal and for the agent to recognize a desired target object. 
    Tying these various modalities together relates to the task of grounded language understanding, in which natural language is used as a query against objects in a physical environment, allowing a real-world, intuitive mechanism by which users can instruct physical agents to engage in tasks such as object retrieval.
    However, current work has neglected the real-world constraint that sensors fail: hardware can become damaged or shipped with defects, sensors can get blocked or obstructed, and various adverse but not uncommon conditions that remove a modality from use. For practical applications, we need mechanisms for accurate object retrieval given that a modality may fail without notice. 
    We demonstrate the usability of our model on a grounded language object retrieval scenario, where an intelligent agent has to select an object given an unconstrained language command. We leverage four modalities including vision, depth sensing, text, and speech, and we show that our model can outperform state-of-the-art contrastive models when modalities are ablated.
\end{abstract}

\settopmatter{printfolios=true} % Page numbers please 
% 9 pages without references.

% \begin{enumerate}
%     \item Objects of five things we select from
%     \item \textcolor{green}{DONE} Adding an overview of the whole process 
%     \item \textcolor{blue}{PROG} Go into more details in section 4 and give examples 
%     \item Move images around
%     \item Quant result section is not complete
%     \item \textcolor{green}{DONE} put the graphs in modality ablation or merge quant and qual
%     \item \textcolor{green}{DONE} add dropping R D graphs
%     \item A paragraph in related work about grounded language 
%     % \item Don't mess with additional experiments
% \end{enumerate}
%===================================================================

\maketitle
% \setcounter{page}{1}

% \section{SIGIR Papers}
% \begin{enumerate}
%     \item \href{https://dl.acm.org/doi/pdf/10.1145/3397271.3401430}{FashionBERT}
%     \item \href{https://dl.acm.org/doi/pdf/10.1145/3397271.3401265?casa_token=W8NqNWp0UQkAAAAA:w-iRUnNhmytDKCUiYzaUPG0bI_yyo8Bzxwro_eOC-zl5VDIGRVT2dvixvnCwLJ0iEKqYo1LkQIWXVA}{CrossBERT}

% \end{enumerate}

@@

Humans use multiple sensory inputs to understand, interact with, and retrieve information from the world around them. It is intuitive that agents learning about the world, upon encountering new concepts and new objects, should form a model that incorporates information from all available sensors and data sources. 
% 
Grounded language understanding, in which natural language is used as a query against objects in a physical environment, allows a real-world, intuitive mechanism by which users can instruct physical agents to engage in tasks such as object retrieval. Visuolinguistic approaches to such object inference tasks typically involve training on large pools of image/text pairs and then using language to subselect elements of the sensed environment~\cite{hong2021gilbert}. Although physical agents such as robots typically have access to sensory and interactive modalities beyond vision, and learning from multiple modalities can improve performance on downstream tasks, most approaches use at most two sensory inputs (e.g., visual data such as RGB images) with single labels, such as those provided by textual natural language. Simultaneously using additional inputs from different modalities is an underexplored area, in part due to the domain-specific nature of such \textit{n}-ary learning approaches. With the modern proliferation of audio and text based communication and proliferation of home agents (e.g., iRobot vacuums and Alexa/Google Home), there is a growing need to handle more modalities, and simultaneously their potential failures.

One difficulty with working with complex multimodal data is the increased likelihood that one or more modalities may have missing information. Current multimodal approaches are typically not robust to the loss of one or more modalities at test time, as may happen if, for example, a physical agent fails to retrieve data from a particular sensor. In order to fully leverage multimodal training data while being robust to missing information, we propose a generalized distance-based loss function that can be extended to learn retrieval models that incorporate an arbitrary number of modalities.

@@

The high level goal of this work is to take arbitrary input modalities about novel objects, including both spoken and written language, and build a model that allows a system to correctly retrieve that object given a subset of those input modalities. This is a generalization of approaches to grounded language learning in which specific input modalities are labeled with language to allow for future identification, but explicitly seeks to be agnostic about the nature of the individual sensory and linguistic inputs. Our contributions are as follows:
\begin{enumerate}
    \item Proposing a general distance-based loss function formulation for multimodal learning that can be extended to an arbitrary number of modalities.
    \item Outperforming state-of-the-art contrastive learning models when one or more modalities are ablated at test time, demonstrating robustness in the face of missing information.
    % \item Outperforming state-of-the-art models for grounded language learning by differentiating visual input modalities such as RGB and depth, rather than combining them into a single modality.
    \item Demonstrating the separate utility of speech and text as sources of label information by treating them as sensory input modalities, rather than explicitly as labels.
\end{enumerate}

The remainder of this paper is organized as follows. In \cref{sec:Related-Work}, we describe existing work on visuolinguistic retrieval, contrastive learning, and multimodal learning. In \cref{sec:Problem-Description}, we formalize the object retrieval problem and give examples of the data under consideration. In \cref{sec:Method}, we describe our novel approach to learning models of linguistically-driven queries against a multimodal set of objects. Finally, in \cref{sec:Experiments}, we demonstrate the effectiveness of our approach against traditional contrastive learning and supervised contrastive learning baselines, both for the general learning problem and in the case of missing information at test time.

@@

There is extensive work on the task of image retrieval, of which physical object retrieval can be considered a special case. In this task, language is used to formulate queries against datasets of images, for example in text-and-image matching tasks for fashion data~\cite{gao2020fashionbert, wen2021comprehensive}, sketch retrieval~\cite{huang2017deep}, and general photographs of objects~\cite{ma2020large, novak2015large, hong2021gilbert}. Prior work has focused solely on language and visual modalities, using text or a combination of language and vision to perform visual retrieval~\cite{vo2019composing}. While recent works have focused on grounding with respect to a knowledge set \cite{10.1145/3357384.3357889,10.1145/3397271.3401097}, our work focuses on robust multimodal learning over to perform grounding over an arbitrary number of input modalities.

The growing number of datasets that contain modalities beyond images and text demonstrates the importance and the challenge of this task. \citet{bagher-zadeh-etal-2018-multimodal} introduce a large dataset of multimodal opinion sentiment and emotion intensity (CMU-MOSEI) for sentiment analysis and emotion recognition. They also introduce a novel multimodal fusion technique called the Dynamic Fusion Graph (DFG).~\citet{GoLD_UMBC} present a multimodal dataset of household objects containing RGB images, depth images, written language, and spoken language, which has been used to support learning grounded language directly from speech given small datasets~\cite{KebeAAAI2022}. 
\citet{baltrusaitisMultimodalMachineLearning2019} propose a new taxonomy of multimodal machine learning by introducing five technical challenges in addition to typical early and late fusion categorization. They cover different approaches to multimodal machine learning such as \textit{representation}, \textit{translation}, \textit{alignment}, \textit{fusion}, and \textit{co-learning}. In this project, we focus on alignment, the process of identifying the direct relationship between elements across modalities.

@@

Another related approach is contrastive learning~\cite{qin2021world}, which is based on the idea of similarity and distance of elements of training data~\cite{NEURIPS2020_supervised_contrastive,chen2020simple}. Triplet loss is also a special case of contrastive loss~\cite{NEURIPS2020_supervised_contrastive}. Contrastive loss is mostly used in self-supervised learning~\cite{bui2021self, alayrac2020self,chen2020simple}, with the exception of \citet{NEURIPS2020_supervised_contrastive}, who use contrastive loss for a supervised problem. Most of these methods are implemented for a non-multimodal dataset (e.g., RGB images only). Our work is a specialization of contrastive loss that is focused on the multimodal input and- language problem.

@@

Some of the most closely related work focuses on learning based on more than two input modalities. \citet{Veit_2018_CVPR} train a joint model of images, hashtags, and users to perform image retrieval. Their task is similar to ours---given a description, we want to find the image/object in the scene that best matches the description. They tackle this problem by forming a three-way tensor product model. They use a ranking loss to train the model where the score of an observed triplet is higher than an unobserved triplet. They sample six negative triplets per positive sample triplet, and use each of them as a negative in the loss. The downstream retrieval task is then simply done by taking the argmax of the tensor product for a given user. This work differs from ours in that it becomes computationally complex as more and higher-dimensional modalities are added.

\citet{semihet_three_way_Lei_2020} use inputs from three modalities of image, sketch, and edgemap to perform image retrieval given the sketch. They use co-attention mechanism, and their loss function contains alignment loss, cross-entropy loss, and sketch-edgemap contrastive loss. \citet{Mittal2020M3ER} use Canonical Correlational Analysis (CCA) to differentiate between ineffective and effective modalities for the emotion recognition task from multiple input modalities including face, speech, and text. Multimodal learning has been used for different applications including but not limited to object retrieval. \citet{Deception_ICMI_2014} use language, physiological response, and thermal sensing to detect deceit. \citet{het_data_fusion_liu_IEEE_2017} take two modalities as input and output predictions in a third modality. \citet{tursun2021efficient} uses quadruplet loss for two modalities only; image and sketch. A quadruplet is composed of a sketch picture as an anchor, a negative example from sketch domain, a negative example from picture domain,  and a positive example from picture domain. \citet{chen2017beyond} also uses quadruplet loss, but does not support multiple domains. In contrast, our method is not restricted to two modalities.
% \todo[inline]{talk about CLIP and DALL-E here}

To the best of our knowledge, there has been limited work on incorporating more than three modalities into a general learning approach. Our proposed loss function closely resembles work on quadruplet loss~\cite{chen2017beyond,tursun2021efficient} but is intended to scale to an arbitrary number of modalities.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=.99\columnwidth]{Figures/experiment-setup.png}
\caption{
The experimental object retrieval setup, in which objects are represented by four modalities: an RGB image, a depth image, spoken descriptions, and textual descriptions. Given a query in some modality, our approach seeks to select the object that is the best fit, per a trained model. This approach, detailed in \cref{sec:Method}, is able to rank objects as to appropriateness even when one or more modalities is ablated at test time (e.g., textual descriptions are missing), and outperforms state-of-the-art contrastive learning approaches on this task.
}
\label{fig:experimental-setup}
\end{figure}

@@

In keeping with previous work on the closely related problem of image retrieval, we focus on contrastive loss approaches, in which the goal is to learn an embedding of data in which similar samples---in our case, samples belonging to the same class of object---are embedded `close' to one another, while dissimilar samples are farther apart. We develop a novel loss function that simultaneously minimizes intra-class distances and maximizes inter-class distances across each pair of modalities, yielding a model that is both effective at the retrieval task defined above and robust to modality dropouts at test time.

\subsection{Distance-based Loss}
\label{ssec:distanceloss}

For $M$ modalities, we define a distance-based loss function which can be used for arbitrary number of modalities. Our proposed method is an extension of the well-known similarity-based triplet loss~\cite{Carvalho-cooking-triplet,triplet_loss_2021_CVPR}, and is similar to contrastive loss~\cite{chen2020simple,NEURIPS2020_supervised_contrastive} under some settings.
Triplet loss-based learning works by forcing similar concepts from different domains `together' in some shared embedding space, while forcing dissimilar concepts `apart.' It is so named because it relies on three data points from the training set: a positive, a negative, and an anchor point. In our setting, the anchor and positive instances are from the same class, but in different modalities.

>>>>

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

% My Packages
\usepackage{cleveref}
\usepackage{comment}
\usepackage{todonotes}
\newcommand{\todokdinline}[1]{\todo[color=red!20,inline]{{KD: \small #1}}}
\newcommand{\todokd}[1]{\todo[color=red!20]{{\small #1 -- Kasra}}}
% \newcommand{\todocainline}[1]{\todo[color=yellow!20,inline]{{CA: \small #1}}}
\newcommand{\todocm}[1]{\todo[color=green!40]{\small #1 -- Cynthia}}
\newcommand{\todocmi}[1]{\todo[inline,color=green!40]{\small #1 -- Cynthia}}
\newcommand{\todoff}[1]{\todo[color=blue!20]{\small #1 -- Frank}}
\newcommand{\todoffinline}[1]{\todo[inline,color=blue!20]{\small #1 -- Frank}}
\newcommand{\todoed}[1]{\todo[color=cyan!20]{\small #1 -- Ed}}

\newcommand{\CitationNeeded}[1]{{\textbf {\color{red}Cite #1}}}
\newcommand{\ProofRead}[1]{{\textbf {\color{red}Proofread please #1}}}
\newcommand{\Complete}[0]{{\textbf {\color{red}Complete it }}}
\newcommand{\Rephrase}[1]{{\textbf {\color{red}Rephrase please #1}}}
\newcommand{\TD}[1]{{\color{red}{\textbf{TODO}}} #1}
\newcommand{\OK}[1]{{\color{green}{\textbf{DONE}}} #1}
\newcommand{\ours}{\textsc{EMMA}}
% \newcommand{\ours}{\textsc{EMMA}}
\newcommand{\geom}{\textsc{Geometric Alignment}}
\newcommand{\supcon}{\textsc{SupCon}}

%%%%%%%%%%%%%%%%%%%%
% EDITING LINK: 
% https://www.overleaf.com/3575751412sjsdmszkxsyh
%%%%%%%%%%%%%%%%%%%%

\title{Multimodal Contrastive Learning for Object Retrieval in the Face of Modality Failures \\ Extended Multimodal Alignment \\ Combining Geometric and classification ... }

% Authors must not appear in the submitted version. They should be hidden
% as long as the tmlr package is used without the [accepted] or [preprint] options.
% Non-anonymous submissions will be rejected without review.

\author{\name Kyunghyun Cho \email kyunghyun.cho@nyu.edu \\
      \addr Department of Computer Science\\
      University of New York
      \AND
      \name Raia Hadsell \email raia@google.com \\
      \addr DeepMind
      \AND
      \name Hugo Larochelle \email hugolarochelle@google.com\\
      \addr Mila, Universit\'e de Montr\'eal \\
      Google Research\\
      CIFAR Fellow}

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{MM}  % Insert correct month for camera-ready version
\def\year{YYYY} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

@@

\maketitle

@@

    We propose a generalized geometric combined with cross-entropy loss function that can be used to learn retrieval models that incorporate an arbitrary number of views of a particular piece of data, and compounded by the challenge of retrieval when a modality becomes unavailable. 
    \todoff{this red text can (should) be shortened}
    \todokd{I shortened it. Please remove both notes if it's resolved}
    {\color{red}Our study is motivated by needs in robotics and computer-human interaction, where an agent has many sensors and thus modalities in which a human may interact both to communicate a desired goal and for the agent to recognize a desired target object.
    Tying these various modalities together relates to the task of grounded language understanding. However, there has been little research on integrating more than two modalities.
    % \todokdinline{Duplicate, it's already mentioned in intro}in which natural language is used as a query against objects in a physical environment, allowing a real-world, intuitive mechanism by which users can instruct physical agents to engage in tasks such as object retrieval.
    % However, current work has neglected the real-world constraint that sensors fail. For practical applications,
    %  we need mechanisms for accurate object retrieval given that a modality may fail without notice.
    }
    % \todoff{There's very little in here about actual method or conclusions}
    There has been widely popular works on self-supervised contrastive learning based on cross-entropy, but there is an entire other approach based on explicit geometric alignment. However, there has been no work on combining the two approaches for multimodal learning to the best of our knowledge. We propose to combine the two approaches and argue that the two are complementary.
    We demonstrate the usability of our model on a grounded language object retrieval scenario, where an intelligent agent has to select an object given an unconstrained language command. 
    We leverage four modalities including vision, depth sensing, text, and speech, and we show that our model can outperform state-of-the-art contrastive learning models by $2\%$ while converging/learning/training $5$ times faster (takes $80\%$ less time or is $20\%$ of the baseline).
    %when modalities are ablated. 
    The code will be publicly available on GitHub and will be included for the camera-ready version (it is redacted for anonymity). 
\end{abstract}

@@

\todoffinline{nix this first sentence and revise the start of the second. We're not doing any cogsci-y stuff, or even human studies tied to modality deprivation. You could take most of the red text in the abstract I mentioned should be compressed and rework it here}
\todokdinline{I took a shot at nixing it. Please remove both notes if it's resolved. I don't get the vibe of cogsci-y stuff or human studies from the first paragraph, would you please refer to those sentences?}
Humans successfully use multiple sensory inputs to understand, interact with, and retrieve information from the world around them. Inspired by the multimodal nature of human interactions with the world, it is intuitive that agents learning about the world, upon encountering new concepts and new objects, should form a model that incorporates information from all available sensors and data sources. Benefits of integrating multiple modalities is twofold; first, additional modalities can help in the cases when other modalities fail, and second, complementary information can be extracted from different modalities that can help with understanding the world.
% 
Grounded language understanding, in which natural language is used as a query against objects in a physical environment, allows a real-world, intuitive mechanism by which users can instruct physical agents to engage in tasks such as object retrieval. Visuolinguistic approaches to such object inference tasks typically involve training on large pools of image/text pairs and then using language to subselect elements of the sensed environment~\cite{hong2021gilbert,Zhuge_2021_CVPR_VLP}.
\todoffinline{Unless Hong et al is a review paper, add at least one more citation}
\todokdinline{I believe this sentence was added to cite some relevant work from SIGIR, so we can remove it. However, I added one more citation anyway.}
Although physical agents such as robots typically have access to sensory and interactive modalities beyond vision, and learning from multiple modalities can improve performance on downstream tasks, most approaches use at most two sensory inputs (e.g., visual data such as RGB plus depth images) with single labels, such as those provided by textual natural language. Simultaneously using additional inputs from different modalities is an underexplored area, in part due to the domain-specific nature of such \textit{n}-ary learning approaches. With the modern proliferation of audio and text based communication and home agents (e.g., Alexa/Google Home), there is a growing need to handle more modalities, and simultaneously their potential failures.

One difficulty with working with complex multimodal data is the increased likelihood that one or more modalities may have missing information; hardware can become damaged or shipped with defects, sensors can get blocked or obstructed, and various adverse but not uncommon conditions that remove a modality from use.
Current multimodal approaches are typically not robust to the loss of one or more modalities at test time, as may happen if, for example, a physical agent fails to retrieve data from a particular sensor. In order to fully leverage multimodal training data while being robust to missing information, we propose a generalized distance-based loss function that can be extended to learn retrieval models that incorporate an arbitrary number of modalities.

@@

\todoff{revise this goal. It sets up the reviewers to take the easy way out and say results are too incremental}
The high-level goal of this work is to take arbitrary input modalities about novel objects, including both spoken and written language, and build a model that allows a system to correctly retrieve that object given a subset of those input modalities. This is a generalization of approaches to grounded language learning in which specific input modalities are labeled with language to allow for future identification, but explicitly seeks to be agnostic about the nature of the individual sensory and linguistic inputs. Our contributions are as follows:
\begin{enumerate}
    \item Proposing a new approach to multimodal learning by combining geometric and cross-entropy based methods and showing that it outperforms and converges faster compared to each method separately.
    % \item Outperforming state-of-the-art models for grounded language learning by differentiating visual input modalities such as RGB and depth, rather than combining them into a single modality.

    \item Our method can be easily extended to an arbitrary number of modalities.\todoffinline{potential counter: isn't the method quadratic?}
    \todokdinline{Yes, but nonetheless it can be extended.}

    \item Outperforming state-of-the-art contrastive learning~\cite{chen2020simple} and supervised contrastive learning~\cite{NEURIPS2020_supervised_contrastive} models by $2\%$ when all modalities are available, and achieving the peak performance $5$ times faster than both methods. 
    % Ours takes 8 epochs, baselines take 40 epochs.
    \todokdinline{Should we break this contribution into two contributions, one for faster learning and the other for performance compared to both supcon and vanilla contrastive learning?}

    \item Demonstrating robustness in the face of missing information, when one or more modalities are ablated at test time.

    \item Demonstrating the separate utility of speech and text as sources of label information by treating them as sensory input modalities, rather than explicitly as labels.

    % \item Stable model that outperforms state-of-the-art contrastive learning models when batch size decreases.\todoff{add motivation in the intro about why robustness to a smaller batch size is important}

\end{enumerate}

% \todoffinline{Super pet peeve of mine: except for books or theses, don't take up space with this roadmap. Instead, in the above contributions, add pointers to the sections (or even subsections) where we provide evidence for each contribution}
% \todokdinline{I think Cynthia added this part for the last submission since we were short a few sentences to reach the page limit. We can remove this.}
% The remainder of this paper is organized as follows. In \cref{sec:Related-Work}, we describe existing work on visuolinguistic retrieval, contrastive learning, and multimodal learning. In \cref{sec:Problem-Description}, we formalize the object retrieval problem and give examples of the data under consideration. In \cref{sec:Method}, we describe our novel approach to learning models of linguistically-driven queries against a multimodal set of objects. Finally, in \cref{sec:Experiments}, we demonstrate the effectiveness of our approach against traditional contrastive learning and supervised contrastive learning baselines, both for the general learning problem and in the case of missing information at test time.

@@

\todoffinline{use paragraphs to add some light structure to this block-o-text}

\todoffinline{I'm not convinced this section shouldn't appear toward the end of the paper. Maybe adding that narrative structure will help?}

There is extensive work on the task of image retrieval, of which physical object retrieval can be considered a special case. In this task, language is used to formulate queries against datasets of images, for example in text-and-image matching tasks for fashion data~\cite{gao2020fashionbert, wen2021comprehensive}, sketch retrieval~\cite{huang2017deep}, and general photographs of objects~\cite{ma2020large, novak2015large, hong2021gilbert}. Prior work has focused solely on language and visual modalities, using text or a combination of language and vision to perform visual retrieval~\cite{vo2019composing}. While recent works have focused on grounding with respect to a knowledge set \cite{10.1145/3357384.3357889,10.1145/3397271.3401097}, our work focuses on robust multimodal learning to perform grounding over an arbitrary number of input modalities.

The growing number of datasets that contain modalities beyond images and text demonstrates the importance and the challenge of this task. \citet{bagher-zadeh-etal-2018-multimodal} introduce a large dataset of multimodal opinion sentiment and emotion intensity (CMU-MOSEI) for sentiment analysis and emotion recognition. They also introduce a novel multimodal fusion technique called the Dynamic Fusion Graph (DFG).~\citet{GoLD_UMBC} present a multimodal dataset of household objects containing RGB images, depth images, written language, and spoken language, which has been used to support learning grounded language directly from speech given small datasets~\cite{KebeAAAI2022}. 
\citet{baltrusaitisMultimodalMachineLearning2019} propose a new taxonomy of multimodal machine learning by introducing five technical challenges in addition to typical early and late fusion categorization. They cover different approaches to multimodal machine learning such as \textit{representation}, \textit{translation}, \textit{alignment}, \textit{fusion}, and \textit{co-learning}. In this work, we focus on alignment, the process of identifying the direct relationship between elements across modalities.

@@

In general there are two different family of approaches to multimodal learning in the literature. One family is based on classification and cross-entropy losses such as~\citet{NEURIPS2020_supervised_contrastive, chen2020simple} and the other family is geometric based such as~\citet{ICML22GeometricMultimodal,Carvalho-cooking-triplet,salvador2017cooking,triplet_loss_2021_CVPR}.
In this paper we propose to marry the two families and show that combining geometric approach with cross-entropy method is superior. \todokdinline{Pun intended :-)}
\todokdinline{Should we move the following two paragraphs to the Approach section?}
For the classification part of our loss function we employ the supervised contrastive loss proposed by~\citet{NEURIPS2020_supervised_contrastive}. The way we formulate our geometric part of the loss function is similar to lifted structured loss~\cite{songCVPR16LiftedStructured}, where they take a geometric approach in a unimodal scenario and consider pairwise distances among all items in a batch, but in this paper we apply our idea to four modalities, and our formulation can be extended to any number of modalities.
This extended geometric formulation results in a loss function that is similar to \citet{ICML22GeometricMultimodal} where they propose a geometric contrastive learning approach in which they %use the same instance of an MLP network (same weights) after extracting embeddings from each modality, while we use different instances of the same MLP network (different weights). They also 
fuse all embeddings as a central embedding and then minimize the distance between each embedding and that central embedding. However, their method does not take into account any notion of classification.

The geometric approach is also known as contrastive learning~\cite{qin2021world}, which is based on the idea of similarity and distance of elements of training data~\cite{Carvalho-cooking-triplet,triplet_loss_2021_CVPR,salvador2017cooking}. Triplet loss is also a special case of contrastive loss~\cite{NEURIPS2020_supervised_contrastive}. Contrastive loss is mostly used in self-supervised learning~\cite{bui2021self, alayrac2020self,chen2020simple}, with some exceptions such as \citet{NEURIPS2020_supervised_contrastive}, who use contrastive loss for a supervised problem. Most of these methods are implemented for a non-multimodal dataset (e.g., RGB images only). Our work is a specialization of contrastive loss that is focused on the multimodal input and- language problem.

@@

Some of the most closely related work focuses on learning based on more than two input modalities. \citet{Veit_2018_CVPR} train a joint model of images, hashtags, and users to perform image retrieval. Their task is similar to ours---given a description, we want to find the image/object in the scene that best matches the description. They tackle this problem by forming a three-way tensor product model. They use a ranking loss to train the model where the score of an observed triplet is higher than an unobserved triplet. They sample six negative triplets per positive sample triplet, and use each of them as a negative in the loss. The downstream retrieval task is then simply done by taking the argmax of the tensor product for a given user. This work differs from ours in that it becomes computationally complex as more and higher-dimensional modalities are added.
Our proposed geometric loss function resembles work on quadruplet loss~\cite{chen2017beyond,tursun2021efficient} but is intended to scale to an arbitrary number of modalities.

\citet{semihet_three_way_Lei_2020} use inputs from three modalities of image, sketch, and edgemap to perform image retrieval given the sketch. They use co-attention mechanism, and their loss function contains alignment loss, cross-entropy loss, and sketch-edgemap contrastive loss. \citet{Mittal2020M3ER} use Canonical Correlational Analysis (CCA) to differentiate between ineffective and effective modalities for the emotion recognition task from multiple input modalities including face, speech, and text. Multimodal learning has been used for different applications including but not limited to object retrieval. \citet{Deception_ICMI_2014} use language, physiological response, and thermal sensing to detect deceit. \citet{het_data_fusion_liu_IEEE_2017} take two modalities as input and output predictions in a third modality. \citet{tursun2021efficient} uses quadruplet loss for two modalities only; image and sketch. A quadruplet is composed of a sketch picture as an anchor, a negative example from sketch domain, a negative example from picture domain,  and a positive example from picture domain. \citet{chen2017beyond} also uses quadruplet loss, but does not support multiple domains. In contrast, our method is not restricted to two modalities.
% \todo[inline]{talk about CLIP and DALL-E here}
To the best of our knowledge, there has been limited work on incorporating more than three modalities into a general learning approach.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=.5\columnwidth]{Figures/experiment-setup.png}
\caption{
The experimental object retrieval setup, in which objects are represented by four modalities: an RGB image, a depth image, spoken descriptions, and textual descriptions. Given a query in some modality, our approach seeks to select the object that is the best fit, per a trained model. This approach, detailed in \cref{sec:Method}, is able to rank objects as to appropriateness even when one or more modalities is ablated at test time (e.g., depth inputs are missing), and outperforms state-of-the-art contrastive learning approaches on this task.
}
\label{fig:experimental-setup}
\end{figure}

@@

In keeping with previous work on the closely related problem of image retrieval, we focus on contrastive loss approaches, in which the goal is to learn an embedding of data where similar samples---in our case, samples belonging to the same class of object---are embedded `close' to one another, while dissimilar samples are farther apart. We develop a novel geometric loss function that simultaneously minimizes intra-class distances and maximizes inter-class distances across each pair of modalities yielding a model that is both effective at the retrieval task defined above and robust to modality dropouts at test time. We take an additional step and combine this geometric loss with a classification-based (cross-entropy) loss function which results in a superior model compared to either of geometric or cross-entropy losses alone.

\subsection{Geometric Alignment Loss}
\label{ssec:distanceloss}
